Data preparation

### 2019-12-13 data-prep.Rmd
arreglo de codificación educación
arreglo de codificación educación

dat09 <- mutate(dat09, educ_rec = car::recode(dat09$cl_degr, "0:3 = 1; 4:5 = 2; 7=2; 6 =3;8:9=4"))             
dat09$educ_rec <- car::recode(dat09$educ_rec,"c(99)=NA",as.numeric = TRUE)

>>>>

dat09 <- mutate(dat09, educ_rec = car::recode(dat09$cl_degr, "0:4 = 1; 5:6 = 2; 8=2; 9 =3;8:7=4"))             
dat09$educ_rec <- car::recode(dat09$educ_rec,"c(99)=NA",as.numeric = TRUE)
